---
title: "BiomeBGC_validationFluxTower"
author: 
  - Dominique Caron
  - Céline Boisvenue
date: "February 2026"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold", message = FALSE)
```

# Overview

Compares Biome-BGC gross primary productivity predictions to Eddy covariance flux tower's estimates.

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("BiomeBGC_validationFluxTower", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

Usually, the module is used with `BiomeBGC_dataPrep` and `BiomeBGC_core`. The needed inputs are the flux tower data which needs to be downloaded (e.g., through AmeriFlux). The user also needs to provide the tower coordinates.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("BiomeBGC_validationFluxTower", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("BiomeBGC_validationFluxTower", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Inputs can be prepared by `BiomeBGC_core` and `BiomeBGC_dataPrep`.